---
title: "Study Summary Figure"
author: "Yaamini Venkataraman"
date: "11/25/2019"
output: github_document
---

In this script, I will create a figure that summarizes the findings from studies used to review the impact of ocean acidification on marine invertebrate reproductive processes before embryonic development. The three individual figures will be arranged into a multipanel plot in InDesign.

# Set up R Markdown Document 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/yaaminivenkataraman/Documents/paper-oa-reproduction-review/metadata/2-metadata/") #Set root directory
```

# Install packages

```{r}
#Install packages
#install.packages("RColorBrewer") #Create color palettes
#install.packages("dichromat") #Color-blind simulation
#install.packages("dplyr") #Data manipulation
#install.packages("reshape2") #Melt and cast data frames
#install.packages("ggplot2") #Plotting
#install.packages("scatterpie") #Pie chart map
```

```{r}
#Load packages
require(RColorBrewer)
require(dichromat)
require(dplyr)
require(reshape2)
require(ggplot2)
require(scatterpie)
```

#Session information

```{r}
sessionInfo()
```

# Reproduction category

## Import and format data

```{r}
findingSummary <- read.csv("Reproduction-Category.csv") #Import data
findingSummary <- findingSummary[,c(1, 2, 5, 3, 4, 6)]
head(findingSummary) #Confirm import
```

```{r}
#Create data subsets for each reproduction category
matingBehavior <- subset(findingSummary, subset = findingSummary$Category == "Mating Behavior")
fertilization <- subset(findingSummary, subset = findingSummary$Category == "Fertilization")
gametogenesis <- subset(findingSummary, subset = findingSummary$Category == "Gametogenesis")
resourceAllocation <- subset(findingSummary, subset = findingSummary$Category == "Resource Allocation")
timing <- subset(findingSummary, subset = findingSummary$Category == "Reproductive Timing and Synchronization")
sexDetermination <- subset(findingSummary, subset = findingSummary$Category == "Sex Determination")
head(sexDetermination) #Examine one subset dataset
```

```{r}
#Make type row namee, then remove category and type columns
rownames(matingBehavior) <- matingBehavior[,6]
matingBehavior <- matingBehavior[,-c(1,6)]
matingBehavior <- matingBehavior[c(3,2,1),]

rownames(fertilization) <- fertilization[,6]
fertilization <- fertilization[,-c(1,6)]
fertilization <- fertilization[c(3,2,1),]

rownames(gametogenesis) <- gametogenesis[,6]
gametogenesis <- gametogenesis[,-c(1,6)]
gametogenesis <- gametogenesis[c(3,2,1),]

rownames(resourceAllocation) <- resourceAllocation[,6]
resourceAllocation <- resourceAllocation[,-c(1,6)]
resourceAllocation <- resourceAllocation[c(3,2,1),]

rownames(timing) <- timing[,6]
timing <- timing[,-c(1,6)]
timing <- timing[c(3,2,1),]

rownames(sexDetermination) <- sexDetermination[,6]
sexDetermination <- sexDetermination[,-c(1,6)]
sexDetermination <- sexDetermination[c(3,2,1),]

head(matingBehavior) #Confirm changes
```

## Create color scheme

```{r}
barplotColors <- c("grey90", "grey50", "grey10") #Create a red-blue palette with 3 colors to represent positive, neutral, and negative effects of ocean acidification on reproductive processes
barplot(t(t(sexDetermination)), col = barplotColors) #Examine color combinations. White is positive, grey is neutral, black is negative
barplot(t(t(sexDetermination)), col = dichromat(barplotColors)) #Examine color combinations with simulated color-blindness.
```

## Create individual plots

```{r}
barplot(t(t(sexDetermination)), 
        axes = FALSE,
        cex.names = 1.5,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,4), las = 2, col = "grey80", cex = 1.2) #Add y-axis
mtext(side = 2, "Number of Findings", line = 2, cex = 1.5) #Add y-axis label
```

```{r}
barplot(t(t(gametogenesis)), 
        axes = FALSE, 
        cex.names = 1.5,
        space = 0.1,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,22), las = 2, col = "grey80", cex = 1.2) #Add y-axis
mtext(side = 2, "Number of Findings", line = 2, cex = 1.5) #Add y-axis label
```

```{r}
barplot(t(t(resourceAllocation)), 
        axes = FALSE,
        cex.names = 1.5,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,32), las = 2, col = "grey80", cex = 1.2) #Add y-axis
mtext(side = 2, "Number of Findings", line = 2, cex = 1.5) #Add y-axis label
```

```{r}
barplot(t(t(timing)), 
        axes = FALSE, 
        cex.names = 1.5,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,2), las = 2, col = "grey80", cex = 1.2) #Add y-axis
mtext(side = 2, "Number of Findings", line = 2, cex = 1.5) #Add y-axis label
```

```{r}
barplot(t(t(matingBehavior)), 
        axes = FALSE, 
        cex.names = 1.5,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,2), las = 2, col = "grey80", cex = 1.2) #Add y-axis
mtext(side = 2, "Number of Findings", line = 2, cex = 1.5) #Add y-axis label
```

```{r}
barplot(t(t(fertilization)), 
        axes = FALSE, 
        cex.names = 1.5,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,42), las = 2, col = "grey80", cex = 1.2) #Add y-axis
mtext(side = 2, "Number of Findings", line = 2, cex = 1.5) #Add y-axis label
```

## Create multipanel plot

```{r}
pdf("Reproduction-Category-Summary-Barplots.pdf", height = 8.5, width = 11)
par(mfrow = c(3,2), oma = c(1, 5, 2, 0), mar = c(3, 3, 0, 0))

barplot(t(t(sexDetermination)), 
        axes = FALSE, axisnames = FALSE,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,4), las = 2, col = "grey80", cex.axis = 3) #Add y-axis
mtext(side = 2, "Number of Findings", line = 2, cex = 2, outer = TRUE) #Add outer y-axis label
mtext(side = 3, " Sex Determination", adj = 0, line = -1, cex = 1.5) #Add category name
mtext(side = 3, expression(italic("  4 studies")), adj = 0, line = -3, cex = 1.2) #Add total studies

legend(x = 0.05, y = 2.8, 
       legend = c("Positive", "Neutral", "Negative"), cex = 2.3,
       pch = 22, pt.cex = 4.5,
        col = "black",
        pt.bg = rev(barplotColors),
       bty = "n") #Add legend

barplot(t(t(gametogenesis)), 
        axes = FALSE, axisnames = FALSE,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,22), las = 2, col = "grey80", cex.axis = 3) #Add y-axis
mtext(side = 3, " Gametogenesis", adj = 0, line = -1, cex = 1.5) #Add category name
mtext(side = 3, expression(italic("  40 studies")), adj = 0, line = -3, cex = 1.2) #Add total studies

barplot(t(t(resourceAllocation)), 
        axes = FALSE, axisnames = FALSE,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,32), las = 2, col = "grey80", cex.axis = 3) #Add y-axis
mtext(side = 3, " Fecundity", adj = 0, line = -1, cex = 1.5) #Add category name
mtext(side = 3, expression(italic("  35 studies")), adj = 0, line = -3, cex = 1.2) #Add total studies

barplot(t(t(timing)), 
        axes = FALSE, axisnames = FALSE,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,2), las = 2, col = "grey80", cex.axis = 3) #Add y-axis
mtext(side = 3, " Timing", adj = 0, line = -1, cex = 1.5) #Add category name
mtext(side = 3, expression(italic("  4 studies")), adj = 0, line = -3, cex = 1.2) #Add total studies

barplot(t(t(matingBehavior)), 
        axes = FALSE, 
        names.arg = c("N", "C", "E", "M"), cex.names = 2.5,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,2), las = 2, col = "grey80", cex.axis = 3) #Add y-axis
mtext(side = 3, " Mating", adj = 0, line = -1, cex = 1.5) #Add category name
mtext(side = 3, expression(italic("  2 studies")), adj = 0, line = -3, cex = 1.2) #Add total studies

barplot(t(t(fertilization)), 
        axes = FALSE, 
        names.arg = c("N", "C", "E", "M"), cex.names = 2.5,
        col = barplotColors) #Create a stacked barplot using colors in barplotColors. Do not plot any axes and increase font size of x-axis labels
axis(side = 2, at = c(0,42), las = 2, col = "grey80", cex.axis = 3) #Add y-axis
mtext(side = 3, " Fertilization", adj = 0, line = -1, cex = 1.5) #Add category name
mtext(side = 3, expression(italic("  54 studies")), adj = 0, line = -3, cex = 1.2) #Add total studies

dev.off()
```

# Year published

## Import and format data

```{r}
yearPublished <- read.csv("Year-Published.csv", header = TRUE) #Import data
yearPublished <- yearPublished[-1,] #Remove 1924 data
head(yearPublished) #Confirm import
```

## Create color scheme

```{r}
yearColors <- RColorBrewer::brewer.pal(4, "RdBu") #Create a red-blue palette with 4 colors to represent each taxa

#Add simulated color-blindness. Will need to change line type for addtional contrast
plot(yearPublished$totCnidarian, type = "l", col = dichromat(yearColors[1]), ylim = c(0,45), lty = 4, lwd = 3)
lines(yearPublished$totEchinoderm, col = dichromat(yearColors[2]), lwd = 3)
lines(yearPublished$totMollusc, col = dichromat(yearColors[3]), lty = 4, lwd = 3)
lines(yearPublished$totCrustacean, col = dichromat(yearColors[4]), lwd = 3)
```

## Create plot

```{r}
pdf("Year-Published-Summary-Line-Plots.pdf", height = 4.25, width = 11)
par(mar = c(5, 6, 3, 1), oma = c(0, 1, 0, 0)) #Change margins

plot(yearPublished$totCnidarian, type = "l", ylim = c(0,45),
     col = yearColors[1], lwd = 3,
     xaxt = "n", yaxt = "n",
     xlab = "", ylab = "",
     xaxs = "i", yaxs = "i") #Plot a line graph with no axes or axis labels
lines(yearPublished$totEchinoderm, col = yearColors[3], lwd = 3) #Add echinoderm information
lines(yearPublished$totMollusc, col = yearColors[4], lwd = 3) #Add mollusc information
lines(yearPublished$totCrustacean, col = yearColors[2], lwd = 3) #Add crustacean information

#Remove black box around plot
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")
box(col = "white")

axis(side = 1, at = 1:17, labels = yearPublished$Year, las = 2, col = "grey80", cex.axis = 2) #Add an x-axis with year information

axis(side = 2, at = seq(0, 40, 10), labels = seq(0, 40, 10), las = 2, col = "grey80", cex.axis = 2) #Add y-axis with paper count information
mtext("Cumulative Publications", side = 2, line = 4.5, cex = 2) #Add a y-axis label

legend("topleft",
       cex = 1.75,
       c("Cnidarian", "Crustacean", "Echinoderm", "Mollusc"),
       lty = rep(1, times = 4), lwd = 3,
       col = yearColors,
       bty = "n")

dev.off()
```

# Location conducted

## Import and format data

```{r}
locationData <- read.csv("Location-Data.csv", header = TRUE) #Import data
tail(locationData) #Confirm import
```

```{r}
locationData <- dcast(locationData, Location + Lat + Long ~ Taxa, value.var = "Count") #Reformat data such that all taxa counts are in separate columns
locationData$Region <- seq(1:length(locationData$Location)) #Add numeric region information
head(locationData) #Confirm reformatting
```

```{r}
scatterpieData <- locationData[,c(3, 2, 8, 4, 6, 7, 5)] #Reorganize columns and subset data needed for pie chart
scatterpieData$Region <- as.factor(scatterpieData$Region) #Make sure everything region is a factor
scatterpieData$Radius <- ((rowSums(x = scatterpieData[,4:7]))/1.5) #Scale pie radius based on number of observations for each region, and divide by 2 so pies are not too large
scatterpieData[which(between(scatterpieData$Radius, 0, 5)),8] <- 5 #Replace any non-zero radius less than 5 with 5 so the radius shows up
head(scatterpieData) #Confirm subset
```

## Create color scheme

```{r}
pieColors <- RColorBrewer::brewer.pal(4, "RdBu") #Create a red-blue palette with 4 colors to represent positive, neutral, and negative effects of ocean acidification on reproductive processes
pieColors
```

## Create map plot

```{r}
#Create base plot to see what pies look like
ggplot() + geom_scatterpie(aes(x = Long, y = Lat, group = Region, r = Radius), data = scatterpieData, cols = colnames(scatterpieData[,4:7]), alpha = 0.8) + coord_equal() + scale_fill_manual(values = pieColors[1:4])
```

```{r}
pdf("Location-Data-Map-Plot.pdf", height = 4.25, width = 11)

world <- map_data('world') #Save worldwide map data

p <- ggplot(world, aes(long, lat)) + #Plot latitude and longitude of world data and save as an object
        geom_map(map=world, aes(map_id=region), fill= "lightgray", color="white") + #Separate regions. Land is grey and oceans are white
        coord_quickmap() + #Quick coordinate system
        theme(panel.background = element_rect(fill = "transparent"), #Remove grey background
              axis.title = element_blank(), #Remove axis labels
              axis.text = element_blank(), #Remove axis text
              axis.ticks = element_blank(), #Remove tick marks
              legend.key.size = unit(1.5, "line"), #Change legend size
              legend.text = element_text(size = 15)) #Change legend text size

p + #Plot the map object
        geom_scatterpie(aes(x = Long, y = Lat, group = Region, r = Radius), data = scatterpieData, cols = colnames(scatterpieData[,4:7]), alpha = 0.8) + #Add pie charts on top with location data. Include legend labels
        scale_fill_manual(values = pieColors[1:4], name = "", ) #Specify legend and pie chart colors and legend title

dev.off()
```

