---
title: "Fertilization Analysis (Final)"
author: "Laura H Spencer"
date: "April 29, 2020"
output: html_document
---

### Load libraries 

```{r setup, message=FALSE, warning=FALSE, results=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("glmmTMB", type="source")

list.of.packages <- c("gsheet", "tidyverse", "janitor", "plotly", "glmmTMB", "metafor", "broom.mixed", "car", "ggpubr", "scales") #add new libraries here 

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Load all libraries 
lapply(list.of.packages, FUN = function(X) {
  do.call("require", list(X)) 
})
sessionInfo()
```

### Prepare data 

NOTE: data is read directly from the GoogleSheet using a share link that was set to "anyone with a link can view"
 
```{r}
# Read in data from GoogleSheet 
data.fert <- as_tibble(gsheet2tbl('https://docs.google.com/spreadsheets/d/111SuH548Et6HDckjbQjtYk-B8A5VfNkUYZgcUNRPxxY/edit?usp=sharing'))

#replace NR (not reported) with NA and convert columns to factor / numeric where needed 
data.fert <- data.fert %>% 
  na_if("NR") %>%     
  clean_names()   %>% # fill in spaces with underscores for column names 
  mutate_at(c('phylum', 'study', 'taxonomic_group', 'common_name', 'latin_name', 'error_statistic'), as.factor) %>%
  mutate_at(c('p_h_experimental', 'p_h_control', 'p_co2_experimental', 'p_co2_control', 'ave_fert_percent_p_h', 'error_percent_p_h', 'number_trials_p_h', 'incubation_time', 'sperm_per_m_l', 'sperm_egg_ratio', 'number_females', 'number_males'), as.numeric) %>%
  mutate(H_experimental=10^(-1*p_h_experimental), 
                     H_control=10^(-1*p_h_control))


#data.fert %>% select(study, ave_fert_percent_p_h, error_percent_p_h, error_statistic, number_trials_p_h) %>% View()

ggplotly(ggplot(data.fert %>% drop_na(phylum)) + geom_violin(aes(x=phylum, y=incubation_time, color=phylum)) + geom_jitter(aes(x=phylum, y=incubation_time, color=phylum, label=study)))
```

### Explore data with figures 

```{r}
ggplotly(
data.fert %>%
ggplot(mapping=aes(x=p_h_experimental, y=ave_fert_percent_p_h, group=taxonomic_group, col=taxonomic_group, text=`common_name`)) + 
  geom_point(size=1.5, width=0.02) +
  facet_wrap(~phylum, scale="free") +
  geom_smooth(method="lm", se=TRUE, aes(fill=taxonomic_group)) +
  ggtitle("Fertilization Rate ~ pH exposure by phylum, linear") +
  theme_minimal() 
)

ggplotly(
data.fert %>%
ggplot(mapping=aes(x=p_h_experimental, y=ave_fert_percent_p_h, group=study, col=study, text=`common_name`)) + 
  geom_point(size=1.5, width=0.02) +
  facet_wrap(~phylum, scale="free") +
  geom_smooth(method="lm", se=TRUE, aes(fill=taxonomic_group)) +
  ggtitle("Fertilization Rate ~ pH exposure by phylum, linear") +
  theme_minimal() 
)

ggplotly(
data.fert %>%
ggplot(mapping=aes(x=p_h_experimental, y=ave_fert_percent_p_h, group=taxonomic_group, col=taxonomic_group, text=`common_name`)) + 
  geom_point(size=1, width=0.02) +
  facet_wrap(~phylum, scale="free") +
  geom_smooth(method="lm", se=TRUE, formula=y ~ poly(x, 2, raw=TRUE), aes(fill=taxonomic_group)) +
  ggtitle("Fertilization Rate ~ pH exposure by phylum, polynomial") +
  theme_minimal()
)
```

### Convert all error values to separate SE & SD columns 

#### 95% Confidence Interval 

Upper 95% CI = Mean + 1.96*SE;  I recorded the difference between the upper 95%CI and the mean (Upper 95%CI - Mean). To convert I will use:  

SE = (Upper 95%CI - Mean) / 1.96  
SD = ((Upper 95%CI - Mean) / 1.96) * sqrt(n)   

#### Standard Deviation / Standard Error conversions 

SE= SD/sqrt(n)   
SD = SE*sqrt(n)  
where n=sample size  

```{r}
data.fert <- data.fert %>% 
  mutate(SE =  case_when(error_statistic == "SD" ~ error_percent_p_h/sqrt(number_trials_p_h), 
         error_statistic == "95% CI" ~ error_percent_p_h/1.96,
         is.na(error_statistic) ~ error_percent_p_h, 
         error_statistic == "SE" ~ error_percent_p_h)) 

data.fert <- data.fert %>% 
  mutate(SD =  case_when(error_statistic == "SE" ~ error_percent_p_h*sqrt(number_trials_p_h), 
         error_statistic == "95% CI" ~ (error_percent_p_h/1.96)*sqrt(number_trials_p_h),
         is.na(error_statistic) ~ error_percent_p_h, 
         error_statistic == "SD" ~ error_percent_p_h)) 
```

### Calculate delta pH (pH experimental - pH control) 

```{r}
data.fert <- data.fert %>% 
  mutate(pH_delta = p_h_experimental-p_h_control)
```

### Convert % fertilization data to proportion fertilized, and replace any values >1 (aka 100% fertilized) with 1 

```{r}
data.fert <- data.fert %>% 
  mutate(ave_fert_proport = case_when(ave_fert_percent_p_h <= 100 ~ ave_fert_percent_p_h/100,
                                      ave_fert_percent_p_h > 100 ~ 1))
```

### Inspect data 

```{r}
data.fert$ave_fert_proport %>% hist()

ggplot(data.fert, aes(group=phylum, col=phylum)) + geom_density(aes(ave_fert_proport))

# How many studies per ~phylum? 
data.fert %>%
  select(phylum, study) %>%
  distinct(phylum, study) %>%
  group_by(phylum) %>% count()

# How many studies per taxonomic group? 
data.fert %>%
  select(phylum, study, taxonomic_group) %>%
  distinct(phylum, study, taxonomic_group) %>%
  group_by(taxonomic_group) %>% count()
```
neg: 12
pos
neut: 123

### Calculate weights for models 

```{r}
weights <- metafor::escalc(measure='MN',
                mi=data.fert$ave_fert_percent_p_h,
                sdi = data.fert$SD,
                ni=data.fert$number_trials_p_h, options(na.action="na.pass"))  
data.fert$w <-weights$vi
```

##  Remove all Crustacean studies, since they do not capture fertilization (all captuer hatch rate)

```{r}
data.fert <- data.fert %>% filter(phylum!="Crustacean")
```

## Remove data from treatments with metal contamination & cocaine
```{r}
# Remove metal contamination
data.fert <- subset(data.fert, !(what_is_2nd_stressor=="Metal Contamination" & data.fert$secondary_stressor=="yes"))
data.fert <- subset(data.fert, !(what_is_2nd_stressor=="Elevated Temperature + Lead (Pb)" & data.fert$secondary_stressor=="yes"))

# Remove cocaine 
data.fert <- subset(data.fert, !(what_is_2nd_stressor=="Cocaine Byproduct" & data.fert$secondary_stressor=="yes"))
```

##  Remove experimental pH values that exceed ambient 

```{r}
data.fert <- data.fert %>% filter(pH_delta<=0)
```


```{r}
# How many studies reported sperm concentratinos? 
data.fert %>%
  filter(!is.na(sperm_per_m_l)) %>% 
  distinct(phylum, study) %>%
  group_by(phylum) %>% count()


# How many studies tested multiple sperm concentrations? 
data.fert %>%
  filter(!is.na(sperm_per_m_l)) %>% 
  distinct(phylum, latin_name, study, sperm_per_m_l) %>% View()
# 5 studies


```

### How many studies per phylum after filtering out those w/o weight calculation? 

```{r}
# Before dropping studies w/o weight calcs
data.fert %>% 
  dplyr::select(phylum, study) %>%
  distinct(phylum, study) %>%
  group_by(phylum) %>% count()
7+36+27

# After dropping studies (final data set for meta-analysis)
data.fert %>% drop_na(w) %>%
  dplyr::select(phylum, study) %>%
  distinct(phylum, study) %>%
  group_by(phylum) %>% count()
6+35+23
```

## INSPECT DATA 

```{r}
as.factor(data.fert$what_is_2nd_stressor) %>% levels()

# What is the pH range? 
data.fert$p_h_experimental %>% summary()
```

### Generate binomial models  

 - Include study as random effect for all models   
 - Include varying combinations of phylum & experimental pH  
 - Decided NOT to include taxa, since so few studies per group  

## Test all candidate covariates alone - are any significant?

## ON MARCH 11 I REPLACE `binomial(link = "logit")` WITH `beta_family(link="logit")`

```{r}
# All data 
summary((drop_na(data.fert, w))$ave_fert_proport)
hist((drop_na(data.fert, w))$ave_fert_proport)

# To use beta model I can't have 0- or 1-inflated data. So, replace instances of 0% fertilization with 0.001%, and 100% with 99.999%
data.fert <- data.fert %>%
  mutate_at("ave_fert_proport", function(x) {
    case_when(
      x == 0 ~ 0.00001,
      x == 1 ~ 0.99999,
      x>0 & x<1 ~ x)})

# Test all candidate predictor variables

# pH alone 
Anova(glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #YES
Anova(glmmTMB(ave_fert_proport ~ p_h_experimental + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #YES

Anova(glmmTMB(ave_fert_proport ~ p_h_control + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ phylum + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ taxonomic_group + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ incubation_time + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l) + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #YES
Anova(glmmTMB(ave_fert_proport ~ log(sperm_egg_ratio) + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_females + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_males + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
```
pH_delta, pH_experimental, and sperm_per_m_l are all significant as sole predictor variables 

## Test all candidate covariates with delta pH - are any significant? 

```{r}
Anova(glmmTMB(ave_fert_proport ~ pH_delta*p_h_control + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ pH_delta*phylum + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #yes interaction effect 
Anova(glmmTMB(ave_fert_proport ~ pH_delta*taxonomic_group + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ pH_delta*incubation_time + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no 
Anova(glmmTMB(ave_fert_proport ~ pH_delta*log(sperm_per_m_l) + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no interaction, but sperm conc. still sign. 
Anova(glmmTMB(ave_fert_proport ~ pH_delta*log(sperm_egg_ratio) + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ pH_delta*number_females + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ pH_delta*number_males + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
```
Significant interactions:  
- pH_delta:phylum                 9.6779  2   0.007915 ** 
- pH_delta:log(sperm_per_m_l)     3.2569  1    0.07112 .  <-- not sign. interaction, but sperm concentration still sign.

## examine main and interaction effects for phylum*pH_delta for all data, and data >7.6

```{r}
Anova(glmmTMB(ave_fert_proport ~ phylum*pH_delta + (1|study), 
                              data=drop_na(data.fert, w), 
                              beta_family(link="logit"), 
                              na.action=na.exclude, weights = 1/(w+1)^2))

Anova(glmmTMB(ave_fert_proport ~ phylum*pH_delta + (1|study), 
                              data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), 
                              beta_family(link="logit"), 
                              na.action=na.exclude, weights = 1/(w+1)^2))
```

## examine main and interaction effects for phylum*log(sperm_per_m_l) for all data, and data >7.6

```{r}
Anova(glmmTMB(ave_fert_proport ~ pH_delta*log(sperm_per_m_l) + (1|study), 
                              data=drop_na(data.fert, w), 
                              beta_family(link="logit"), 
                              na.action=na.exclude, weights = 1/(w+1)^2))

Anova(glmmTMB(ave_fert_proport ~ pH_delta*log(sperm_per_m_l) + (1|study), 
                              data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), 
                              beta_family(link="logit"), 
                              na.action=na.exclude, weights = 1/(w+1)^2))
```

### Identify best model by ANCOVA, with phylum, pH_delta, and log(sperm_per_ml) as candidate covariates

```{r}
# Identify best model using lowest AIC

# covariates individually 
m1 <- glmmTMB(ave_fert_proport ~ pH_delta  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m2 <- glmmTMB(ave_fert_proport ~ log(sperm_per_m_l)  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m3<- glmmTMB(ave_fert_proport ~ phylum  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)

# pH_delta with phylum
m4<- glmmTMB(ave_fert_proport ~ pH_delta*phylum  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m5<- glmmTMB(ave_fert_proport ~ pH_delta:phylum  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m6<- glmmTMB(ave_fert_proport ~ pH_delta + phylum  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m6.1<- glmmTMB(ave_fert_proport ~ phylum + phylum:pH_delta  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m6.2<- glmmTMB(ave_fert_proport ~ pH_delta + phylum:pH_delta  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)

# pH_delta with log(sperm_per-mL)
m7<- glmmTMB(ave_fert_proport ~ pH_delta*log(sperm_per_m_l)  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m8<- glmmTMB(ave_fert_proport ~ pH_delta:log(sperm_per_m_l)  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m9<- glmmTMB(ave_fert_proport ~ pH_delta+log(sperm_per_m_l)  + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)

# All three predictor variables with all interaction
m10 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)

# All three predictor variables, with only some interactions 
m11 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m12 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum - pH_delta:log(sperm_per_m_l) + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m13 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum - pH_delta:log(sperm_per_m_l) - pH_delta:phylum:log(sperm_per_m_l) + 
                      (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m14 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum - pH_delta:log(sperm_per_m_l) - pH_delta:phylum:log(sperm_per_m_l) - 
                      phylum + (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m15 <- glmmTMB(ave_fert_proport ~ pH_delta + log(sperm_per_m_l) + (1|study), 
                    data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
```

# Identify and save best fit model (called "best") to object

```{r}
AIC(m1, m2, m3, m4, m5, m6, m6.1, m6.2, m7, m8, m9, m10, m11, m12, m13, m14, m15) %>% arrange(AIC) #lowest AIC = m5,m6.2

BIC(m5, m4, m6, m1, m6.1, m6.2) %>% arrange(BIC) # Lowet BIC = m5, m6.2

summary(m5)$AICtab["logLik"]
summary(m6.2)$AICtab["logLik"]
summary(m4)$AICtab["logLik"] # <- highest logLik (but barely)

summary(m6.2)$AICtab["deviance"]
summary(m5)$AICtab["deviance"]
summary(m4)$AICtab["deviance"] # <- lowest deviance (but barely)

# Models 5 and 6.2 are equal, and Model 4 is 2nd and because I also want to examine effect of pH as a sole predictor (across taxa) as well as the include a separate intercept for phylum, so I will go with model 4 (fert ~ phylum*pH_delta) 

View(data.fert)
```

```{r}
# All data 
car::Anova(best <- glmmTMB(ave_fert_proport ~ phylum + phylum:pH_delta  + (1|study), 
                           data=drop_na(data.fert, w), beta_family(link="logit"), 
                           na.action=na.exclude, weights = 1/(w+1)^2))
summary(best) #sign. effect of delta pH

# Out of curiosity, what would the equation for each phylum be if I constructed separate models? 
# "Cnidarian"
# Intercept = 0.8060, slope = 2.1697, not sign.
summary(glmmTMB(ave_fert_proport ~ pH_delta  + (1|study), 
                           data=drop_na(data.fert %>% filter(phylum=="Cnidarian"), w), beta_family(link="logit"), 
                           na.action=na.exclude, weights = 1/(w+1)^2))
# "Echinoderm" 
# Intercept = 1.1142, slope = 1.7916, sign.
summary(glmmTMB(ave_fert_proport ~ pH_delta  + (1|study), 
                           data=drop_na(data.fert %>% filter(phylum=="Echinoderm"), w), beta_family(link="logit"), 
                           na.action=na.exclude, weights = 1/(w+1)^2))
# "Mollusc" 
# Intercept = 1.6495, slope = 0.4047, not sign.
summary(glmmTMB(ave_fert_proport ~ pH_delta  + (1|study), 
                           data=drop_na(data.fert %>% filter(phylum=="Mollusc"), w), beta_family(link="logit"), 
                           na.action=na.exclude, weights = 1/(w+1)^2))

#format(1.714e-06, scientific = F, digits = 3)
```
## Plot effects

```{r}
#install.packages("effects")
library(effects)
effects_ok <- (requireNamespace("effects") && getRversion() >= "3.6.0")
if (effects_ok) {
(ae <- allEffects(best))
plot(ae)
}
```

```{r}
Anova(m2)
# Identify best model using lowest AIC and R^2 value
m1 <- glmmTMB(ave_fert_proport ~ pH_delta  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m2 <- glmmTMB(ave_fert_proport ~ log(sperm_per_m_l)  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m3<- glmmTMB(ave_fert_proport ~ phylum  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)

m4<- glmmTMB(ave_fert_proport ~ pH_delta*phylum  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m5<- glmmTMB(ave_fert_proport ~ pH_delta:phylum  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m6<- glmmTMB(ave_fert_proport ~ pH_delta + phylum  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m6.1<- glmmTMB(ave_fert_proport ~ phylum + phylum:pH_delta  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m6.2<- glmmTMB(ave_fert_proport ~ pH_delta + phylum:pH_delta  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)

m7<- glmmTMB(ave_fert_proport ~ pH_delta*log(sperm_per_m_l)  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m8<- glmmTMB(ave_fert_proport ~ pH_delta:log(sperm_per_m_l)  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m9<- glmmTMB(ave_fert_proport ~ pH_delta+log(sperm_per_m_l)  + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)

m10 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m11 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m12 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum - pH_delta:log(sperm_per_m_l) + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m13 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum - pH_delta:log(sperm_per_m_l) - pH_delta:phylum:log(sperm_per_m_l) + 
                      (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m14 <- glmmTMB(ave_fert_proport ~ pH_delta*phylum*log(sperm_per_m_l) - pH_delta:phylum - pH_delta:log(sperm_per_m_l) - pH_delta:phylum:log(sperm_per_m_l) - 
                      phylum + (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
m15 <- glmmTMB(ave_fert_proport ~ pH_delta + log(sperm_per_m_l) + (1|study), 
                    data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)
```

# Identify and save best fit model (called "best") to object

```{r}
AIC(m1, m2, m3, m4, m5, m6, m6.1, m6.2, m7, m8, m9, m10, m11, m12, m13, m14, m15) %>% arrange(AIC) #lowest AIC = m1,m6.2, m5

BIC(m1, m2, m3, m4, m5, m6, m6.1, m6.2, m7, m8, m9, m10, m11, m12, m13, m14, m15) %>% arrange(BIC) # Lowet BIC = m1, m3, m6.2

summary(m1)$AICtab["logLik"]
summary(m6.2)$AICtab["logLik"] # <- highest logLik (but barely)
summary(m5)$AICtab["logLik"] # <- highest logLik (but barely)
summary(m3)$AICtab["logLik"] 

summary(m6.2)$AICtab["deviance"]
summary(m5)$AICtab["deviance"]
summary(m4)$AICtab["deviance"] # <- lowest deviance (but barely)

# Models 1 now has the lowest AIC and BIC 

Anova(m1)
8-0.315
```


```{r}
Anova(best7.6 <- glmmTMB(ave_fert_proport ~ pH_delta + (1|study), 
                              data=subset(drop_na(data.fert, w), p_h_experimental>=7.6), 
                              beta_family(link="logit"), 
                              na.action=na.exclude, weights = 1/(w+1)^2)) 

summary(best7.6)
```


## Test model using [H+] instead of pH 
[H+] converted to ppm 
Yes, interaction in model still significant (although less significant)

```{r}
Anova(glmmTMB(ave_fert_proport ~ phylum + phylum:I(H_experimental*1000000) + 
                (1|study), data=drop_na(data.fert, w), beta_family(link="logit"), 
              na.action=na.exclude, weights = 1/(w+1)^2))
```

## Here I extract best model intercepts and slopes 

```{r}
library(broom)
(best.coef <- tidy(best)) %>% mutate(estimate=round(estimate, digits = 2))
(best7.6.coef <- tidy(best7.6))
```

```{r}
0.92+0.24
0.92+0.21
```


```{r}
summary(best)
```

### Write a function to predict %fertilization at various delta levels (and specifying the model) 

```{r}
#"Cnidarian"
predict.fert.cnid <- function(pH, model) {
    linear.predictor <- as.vector((
      summary(model)$coefficients$cond[,"Estimate"]["(Intercept)"] + 
        summary(model)$coefficients$cond[,"Estimate"]["phylumCnidarian:pH_delta"]*pH))
    predicted <- exp(linear.predictor) / (1+exp(linear.predictor))
    print(predicted)
    #scales::percent(x=predicted, accuracy = .01)
}
# Echinoderm
predict.fert.echin <- function(pH, model) {
    linear.predictor <- as.vector((summary(model)$coefficients$cond[,"Estimate"]["(Intercept)"] + 
                                     summary(model)$coefficients$cond[,"Estimate"]["phylumEchinoderm"] + 
                           summary(model)$coefficients$cond[,"Estimate"]["phylumEchinoderm:pH_delta"]*pH))
    predicted <- exp(linear.predictor) / (1+exp(linear.predictor))
    print(predicted)
    #scales::percent(x=predicted, accuracy = .01)
}
# Mollusc
predict.fert.moll <- function(pH, model) {
    linear.predictor <- as.vector((summary(model)$coefficients$cond[,"Estimate"]["(Intercept)"] + 
                                     summary(model)$coefficients$cond[,"Estimate"]["phylumMollusc"] + 
                           summary(model)$coefficients$cond[,"Estimate"]["phylumMollusc:pH_delta"]*pH))
    predicted <- exp(linear.predictor) / (1+exp(linear.predictor))
    print(predicted)
    #scales::percent(x=predicted, accuracy = .01)
}


# Estimate % fertilization @ various delta pH using hand-typed equation (to double check equation)
# Cnidarians
exp(0.92 + 2.43*0) / (1 + exp(0.92 + 2.43*0)) #@ delta-pH = 0 
exp(0.92 + 2.43*-0.25) / (1 + exp(0.92 + 2.43*-0.2)) #@ delta-pH = -0.25 
exp(0.92 + 2.43*-0.5) / (1 + exp(0.92 + 2.43*-0.3)) #@ delta-pH = -0.5%

# Echinoderms
exp(1.16 + 1.92*0) / (1 + exp(1.16 + 1.92*0)) #@ delta-pH = 0 
exp(1.16 + 1.92*-0.25) / (1 + exp(1.16 + 1.92*-0.2)) #@ delta-pH = -0.25 
exp(1.16 + 1.92*-0.5) / (1 + exp(1.16 + 1.92*-0.3)) #@ delta-pH = -0.5%


# predictions <- data.frame(matrix(ncol=4,nrow=0, dimnames=list(NULL, c("pH", "cnid.predict", "echin.predict", "moll.predict"))))
# x <- seq(from=-1, to=0, by=0.05)
# for (i in 1:length(x)) {
#   predictions[i,1] <- x[i]
#   predictions[i,2] <- predict.fert.cnid(x[i], best)
#   predictions[i,3] <- predict.fert.echin(x[i], best)
#   predictions[i,4] <- predict.fert.moll(x[i], best)
# }
# predictions %>% View()

predictions.RCP <- data.frame(matrix(ncol=4,nrow=0, dimnames=list(NULL, c("pH", "cnid.predict", "echino.predict", "moll.predict"))))
x <- c(-0.065, -0.145, -0.203, -0.31)
for (i in 1:length(x)) {
  predictions.RCP[i,1] <- x[i]
  predictions.RCP[i,2] <- round(predict.fert.cnid(x[i], best) - predict.fert.cnid(0, best), digits = 3)*100
  predictions.RCP[i,3] <- round(predict.fert.echin(x[i], best) - predict.fert.echin(0, best), digits = 3)*100
  predictions.RCP[i,4] <- round(predict.fert.moll(x[i], best) - predict.fert.moll(0, best), digits = 3)*100
}

# When the 7.6 model split up each phylum 
# # predict values from model using only pH values >=7.6
# predictions.RCP.7.6 <- data.frame(matrix(ncol=4,nrow=0, dimnames=list(NULL, c("pH", "cnid.predict", "echino.predict", "moll.predict"))))
# x <- c(-0.065, -0.145, -0.205, -0.315)
# for (i in 1:length(x)) {
#   predictions.RCP.7.6[i,1] <- x[i]
#   predictions.RCP.7.6[i,2] <- round(predict.fert.cnid(x[i], best7.6) - predict.fert.cnid(0, best7.6), digits = 3)*100
#   predictions.RCP.7.6[i,3] <- round(predict.fert.echin(x[i], best7.6) - predict.fert.echin(0, best7.6), digits = 3)*100
#   predictions.RCP.7.6[i,4] <- round(predict.fert.moll(x[i], best7.6) - predict.fert.moll(0, best7.6), digits = 3)*100
# }
# predictions.RCP.7.6 %>% View()
```

### Generate estimates & confidence intervals (log likelihood)

```{r}
confint(best)
confint(best7.6)
```

### Inspect residuals ~ fitted values 

```{r}
aa5 <- augment(best, data=drop_na(data.fert, w))
#ggplotly(
ggplot(aa5, aes(x=.fitted,y=.resid)) + 
    geom_point() + 
  geom_smooth()
#)

aa5.7.6 <- augment(best7.6, data=subset(drop_na(data.fert, w), p_h_experimental>=7.6))
#ggplotly(
ggplot(aa5.7.6, aes(x=.fitted,y=.resid)) + 
    geom_point() + 
  geom_smooth()
#)
```

### Generate model predictions and plot against real data 

```{r}
## For all data 
# First find min and max pH tested per phylum 
ph.min.max <- drop_na(data.fert, w) %>%
  dplyr::select(phylum, pH_delta) %>%
  group_by(phylum) %>%
  summarize(min=min(pH_delta, na.rm=TRUE), max=max(pH_delta, na.rm=TRUE))


# Now generate range of pH levels for each phylum
phylum.list <- list()
for (i in 1:nrow(ph.min.max)) {
  phylum.list[[i]] <- data.frame(ph=c(seq(from=as.numeric(ph.min.max[i,"min"]), 
                            to=as.numeric(ph.min.max[i,"max"]), 
                            by=0.005)),
                   phylum=rep(c(ph.min.max[i,"phylum"]))) %>%
  mutate(ph = as.numeric(formatC(ph, format = "f", digits = 3))) 
}

# Combine range of new pH levels and add study and weight columns each with all NA values 
new.data <- bind_rows(phylum.list) %>% purrr::set_names(c("pH_delta", "phylum")) 
new.data$study <- NA 
new.data$w <- NA 

# Now predict change in fertilization rate for each phylum using our best fit model 
predict.test.df <- predict(best, newdata = new.data, se.fit = T, type="response", re.form = NA)
predict.test.df.df <- predict.test.df %>% as.data.frame() %>%
  cbind(new.data) 
``` 

```{r}
# Do it again for model fit against data >7.6 
ph.min.max.7.6 <- subset(drop_na(data.fert, w), p_h_experimental>=7.6) %>% 
  dplyr::select(phylum, pH_delta) %>% 
  group_by(phylum) %>% 
  summarize(min=min(pH_delta, na.rm=TRUE), max=max(pH_delta, na.rm=TRUE))

phylum.list.7.6 <- list()
for (i in 1:nrow(ph.min.max.7.6)) {
  phylum.list.7.6[[i]] <- data.frame(ph=c(seq(from=as.numeric(ph.min.max.7.6[i,"min"]), 
                            to=as.numeric(ph.min.max.7.6[i,"max"]), 
                            by=0.001)),
                   phylum=rep(c(ph.min.max.7.6[i,"phylum"])))%>%
  mutate(ph = as.numeric(formatC(ph, format = "f", digits = 5))) 
}
new.data.7.6 <- bind_rows(phylum.list.7.6) %>% purrr::set_names(c("pH_delta", "phylum"))
new.data.7.6$study <- NA 
new.data.7.6$w <- NA 

predict.test.df.7.6 <- predict(best7.6, newdata = new.data.7.6, se.fit = T, type="response")
predict.test.df.df.7.6 <- predict.test.df.7.6 %>% as.data.frame() %>%
  cbind(new.data.7.6) 
#scales::show_col(c("#e41a1c","#4daf4a","#ff7f00","#984ea3",'#377eb8'))

predict.test.df.df.7.6 %>% filter(pH_delta%in% c(-0.065, -0.145, -0.203, -0.31)) %>% 
  dplyr::select(-phylum) %>% distinct() %>% arrange(pH_delta) %>% 
  mutate((delta=(predict.test.df.df.7.6 %>% filter(pH_delta==0))$fit[1]-fit)*100)
```

## Double check that my hand calculated predictions for RCP match those predicted using the `predict` function 

```{r}
predict.test.df.df %>% filter(pH_delta == 0)
# Ambient pH predictions 
# Cnidarian:  0.7142389 
# Echinoderm: 0.7599396
# Mollusc:    0.7557047

predict.test.df.df %>% 
  mutate(pH_delta = formatC(pH_delta, format = "f", digits = 3)) %>% 
  filter(pH_delta %in% predictions.RCP$pH) %>% filter(phylum=="Mollusc") %>% dplyr::select(fit)

# pH_delta    Cnidarian:        Echinoderm:       Mollusck:
# ~0            0.7142389       0.7599396         0.7557047
# -0.315                        0.6357550         0.7372109
# -0.205        0.6050407				0.6831409         0.7438751
# -0.145				0.6395422       0.7075419         0.7474631
# -0.065        0.6833471       0.7382934         0.7521950

predict.test.df.df %>% 
  #mutate(pH_delta = formatC(pH_delta, format = "f", digits = 3)) %>% 
  filter(pH_delta %in% predictions.RCP$pH) %>% filter(phylum=="Cnidarian") %>% dplyr::select(pH_delta,fit) %>% 
  mutate(delta_cnid=round(100*(fit-0.7152239), digits = 1))

predict.test.df.df %>% 
  #mutate(pH_delta = formatC(pH_delta, format = "f", digits = 3)) %>% 
  filter(pH_delta %in% predictions.RCP$pH) %>% filter(phylum=="Echinoderm") %>% dplyr::select(pH_delta,fit) %>% 
  mutate(delta_echino=round(100*(fit-0.7621473), digits = 1))

predict.test.df.df %>% 
  #mutate(pH_delta = formatC(pH_delta, format = "f", digits = 3)) %>% 
  filter(pH_delta %in% predictions.RCP$pH) %>% filter(phylum=="Mollusc") %>% dplyr::select(pH_delta,fit) %>% 
  mutate(delta_moll=round(100*(fit-0.7559793), digits = 1))

# The results match!!! 
```

### Figure caption: 

Fertilization success (%) by experimental pH across marine taxa examined in this review. Meta-analysis was performed using a binomial regression model, and indicates that fertilization success decreases with pH across Crustacean (5 studies), Echinoderm (12 studies), and Mollusc (18 studies). Fertilization success was not significantly affected by pH in Cnidarian (4 studies). Each point reflects the average % fertilization reported by one study at an experimental pH. 

### Generate single figure with all phyla - no longer valid 

```{r}
# # Examine pH-experimental significance as predictor using X-squared test  
# Anova(best)
# 
# ggplotly(
# (gg.full <- ggplot() + 
#   geom_jitter(data=drop_na(data.fert, w), aes(x=pH_delta, y=ave_fert_proport, group=phylum, col=phylum, label=study), size=1.2, width=0.03) + #, col="gray40"
#   #facet_wrap(~phylum, scales="free") + 
#   theme_minimal() +
#   ggtitle(NULL) +
#     #ggtitle("A. Fertilization success ~ delta pH with model predictions (full pH range, all taxa)") + 
#   xlab("delta pH") + ylab("Proportion fertilization success") +
#   scale_color_manual(name=NULL, values=c("#ca0020","#92c5de",'#0571b0')) +  #"#f4a582",
#   theme_minimal() + 
#   #coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
#   geom_line(data = predict.test.df.df, aes(x=pH_delta, y=fit), col="gray70") + #, col=phylum
#   geom_ribbon(data = predict.test.df.df, aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), linetype=2, alpha=0.1, col="gray70") + 
#     guides(colour = guide_legend(override.aes = list(size=4))) + 
#   theme(legend.text = element_text(size = 12), legend.position = "top",
#         legend.margin=margin(0,0,0,0),
#         legend.box.margin=margin(-8,-8,-8,-8)) + 
#     #theme(legend.position = "none") +
#   annotate(geom="text", x=-1.53, y=0.83, size=3.5, colour="gray40", label=paste("Full pH range: χ2 p-value =", round(Anova(best)[,"Pr(>Chisq)"], digits =6), sep=" ")))) #add fill=phylum in geom_ribbon aes if color desired 

```

Using only pH values 7.6 and greater - no longer valid 

```{r}
# Anova(best7.6)
# 
# #ggplotly(
# (gg.7.6 <- ggplot() + 
#   geom_jitter(data=subset(drop_na(data.fert, w),p_h_experimental>=7.6), aes(x=pH_delta, y=ave_fert_proport, group=phylum, col=phylum, label=study), size=1.2, width=0.03) + #, col="gray40"
#   #facet_wrap(~phylum, scales="free") + 
#   theme_minimal() +
#   ggtitle(NULL) +
#     #ggtitle("A. Fertilization success ~ delta pH with model predictions (pH>7.6)") + 
#   xlab("delta pH") + ylab("Proportion fertilization success") +
#   scale_color_manual(name=NULL, values=c("#ca0020","#92c5de",'#0571b0')) +  #"#f4a582",
#   theme_minimal() + 
#     theme(legend.position = "none") +
#     #theme(legend.text = element_text(size = 12), legend.position = "top",
#     #    legend.margin=margin(0,0,0,0),
#     #    legend.box.margin=margin(-5,-5,-5,-5)) + 
#     #    guides(colour = guide_legend(override.aes = list(size=4))) + 
#     coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
#     geom_line(data = predict.test.df.df.7.6, aes(x=pH_delta, y=fit), col="gray70") + #, col=phylum
#   geom_ribbon(data = predict.test.df.df.7.6, aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), linetype=2, alpha=0.1, col="gray70") +     annotate(geom="text", x=-.95, y=0.87, size=3.5, colour="gray40", label=paste("pH≥7.6: χ2 p-value =", round(Anova(best7.6)[,"Pr(>Chisq)"], digits =3), sep=" "))) #add fill=phylum in geom_ribbon aes if color desired 
```
```{r}
# alltaxa.plots <- ggarrange(gg.full + ylab(NULL)+ xlab(NULL) + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()), 
#         gg.7.6 + ylab(NULL), ncol=1, nrow=2)
# png(file = "fertilization-all-taxa-20210308.png", width = 600, height=500)
# annotate_figure(alltaxa.plots, left = text_grob("Proportion Fertilization Success", color = "gray20", rot = 90))
# dev.off()
```

## Do both full and 7.6 plots one one

```{r}
# (gg.both <- ggplot() + 
#   geom_jitter(data=drop_na(data.fert, w), aes(x=pH_delta, y=ave_fert_proport, group=phylum, col=phylum, label=study), 
#               size=1.2, width=0.03) + #, col="gray40"
#   ggtitle("(a) All taxa") + 
#   xlab("delta pH") + ylab("Proportion fertilization success") +
#   theme_minimal() +
#   theme(plot.title = element_text(hjust = 0.5, size=13, colour="gray15")) +
#   coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
#    scale_color_manual(name=NULL, values=c("#ca0020","#92c5de",'#0571b0')) +  #"#f4a582",
#   geom_ribbon(data = predict.test.df.df, 
#               aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
#               linetype=9, alpha=0.3, fill="#fff2ae") + 
#      geom_line(data = predict.test.df.df, aes(x=pH_delta, y=fit), 
#             col="gray30", linetype=2) + 
#   theme(legend.position = "none") +
#   #guides(colour = guide_legend(override.aes = list(size=4))) + 
#   geom_label(aes(x=-1.54, y=0.5), label=paste("Model with full pH range:\nχ2 p-value =",
#                        round(Anova(best)[,"Pr(>Chisq)"], digits =6), sep=" "),
#              colour="gray15", size=5, alpha=0.3, fill="#fff2ae") +
#    geom_ribbon(data = predict.test.df.df.7.6, 
#               aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
#               linetype=0, alpha=0.1, fill="springgreen3") +
#    geom_line(data = predict.test.df.df.7.6, 
#                  aes(x=pH_delta, y=fit), 
#                  col="gray30", linetype=1) +
#    geom_label(aes(x=-1.2, y=0.84,
#             label=paste("Model with pH ≥7.6:\nχ2 p-value =", round(Anova(best7.6)[,"Pr(>Chisq)"], digits =3), sep=" ")), 
#             colour="gray15", alpha=0.1, fill="springgreen3", size=5))
# 
# tiff(file = "fertilization-all-taxa-20210510.tiff", width = 1500, height=1000, res=250)
# gg.both
# dev.off()

```




# Examine color scheme (`show_col` is from scales library)

```{r}
show_col(c("#ca0020","#f4a582","#92c5de",'#0571b0'))
#e41a1c = Cnidarian (red)  
#ff7f00 = Crustacean (orange)  
#4daf4a = Echinoderm (green)  
#377eb8 = Mollusc (blue)  

#ca0020 = coral 
#f4a582 = crustacean 
#92c5de = echinoderm
#0571b0 = mollusc
```

### Generate figure: pH data by phylum, each with beta regression model fit + CI 

```{r}
ggplotly(
ggplot() + 
  geom_jitter(data=drop_na(data.fert, w), aes(x=pH_delta, y=ave_fert_proport, group=phylum, col=phylum, label=study), size=1.2, width=0.03, col="gray40") +
  facet_wrap(~phylum, scales="free") + theme_minimal() +
  ggtitle("Fertilization success ~ pH with beta-regression model predictions") + 
  xlab("Experimental pH") + ylab("Proportion fertilization success") +
  #scale_color_manual(name=NULL, values=c("#e41a1c","#ff7f00","#4daf4a",'#377eb8')) +
  theme_minimal() + 
  coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
  geom_line(data = predict.test.df.df, aes(x=pH_delta, y=predict), col="gray50") + #, col=phylum
  geom_ribbon(data = predict.test.df.df, aes(x=pH_delta, ymin=predict-se.fit, ymax=fit+se.fit), linetype=2, alpha=0.1, col="gray50") + theme(legend.position = "none")) #add fill=phylum in geom_ribbon aes if color desired 
```

## Run GLMs on each phylum  and generate plots 

1) Are slopes significantly different from zero? 
2) If so, what is the equation? 

### Cnidarian 

```{r}
Anova(glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ p_h_control + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ incubation_time + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ log(sperm_egg_ratio) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_females + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_males + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no

# DETEREMINE BEST FIT MODEL WITH CANDIDATE PREDICTOR VARIABLES 
AIC(glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) # BEST FIT 
AIC(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l)*pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l):pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l)+pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no

# Best fit is with pH_delta only 
model.cnidarian <- glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"), beta_family(link="logit"), na.action=na.exclude,  weights = 1/(w+1)^2)
Anova(model.cnidarian)
summary(model.cnidarian) 

# Inspect residuals 
aa5 <- augment(model.cnidarian, data=drop_na(data.fert, w) %>% filter(phylum=="Cnidarian"))
ggplot(aa5, aes(x=.fitted,y=.resid)) + 
    geom_point() + 
  geom_smooth()

# NOTE: THERE ARE NO CNIDARIAN STUDIES THAT USED PH < 7.6, SO ONLY HAVE ONE MODEL 

paste("Experimental pH χ2 p-value =", round(Anova(model.cnidarian)[,"Pr(>Chisq)"], digits = 3), sep=" ")

predict.cnidarian <- predict(model.cnidarian, newdata = subset(new.data, phylum=="Cnidarian"), se.fit = TRUE, type="response")
predict.cnidarian.df <- predict.cnidarian %>%
  as.data.frame() %>%
  cbind(subset(new.data, phylum=="Cnidarian"))

(plot.cnidarian <- ggplot() + 
  geom_jitter(data=drop_na(data.fert, w) %>% 
                filter(phylum=="Cnidarian"), aes(x=pH_delta, y=ave_fert_proport), size=1.2, width=0.03, col="#ca0020") +
  ggtitle("(c) Cnidarian") + 
  xlab(NULL) + ylab("Proportion fertilization success") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size=13, colour="gray15")) +
  coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
  geom_ribbon(data = predict.cnidarian.df, aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit),linetype=0, alpha=0.1, fill="springgreen3") + 
  geom_line(data = predict.cnidarian.df, aes(x=pH_delta, y=fit), col="gray30", linetype=1) +
  geom_label(aes(x=-.8, y=0.83,
            label=paste("χ2 p-value =", round(Anova(model.cnidarian)[,"Pr(>Chisq)"], digits = 3), sep=" ")),
            colour="gray15", alpha=0.1, size=5, fill="springgreen3", size=3)) #+
#    annotate(geom = "table",
#           x = -1.9,
#           y = .1,
#           label = list(my_data)))


```

```{r}
(plot.cnidarian <- ggplot() + 
  geom_jitter(data=drop_na(data.fert, w) %>% 
                filter(phylum=="Cnidarian"), aes(x=pH_delta, y=ave_fert_proport), size=1.2, width=0.03, col="#ca0020") +
  ggtitle("(a) Cnidarian") + 
  xlab(NULL) + ylab("Proportion fertilization success") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size=15, colour="gray15"), panel.grid.minor = element_blank()) +
  coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
  geom_ribbon(data = predict.test.df.df %>% filter(phylum=="Cnidarian"), 
              aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit),linetype=0, alpha=0.3, fill="gray70") + 
  geom_line(data = predict.test.df.df %>% filter(phylum=="Cnidarian"), aes(x=pH_delta, y=fit), col="gray30", linetype=1) +
  geom_label(aes(x=-.8, y=0.83,
            label=paste("z-score = ", round(best.coef[best.coef$term=="phylumCnidarian:pH_delta","statistic"], digits = 2), 
                        "\np =", round(best.coef[best.coef$term=="phylumCnidarian:pH_delta","p.value"], digits = 2), sep=" ")),
            colour="gray25", alpha=0.3,  fill=NA, size=4, label.size = NA))
```


### Echinoderm

```{r}
Anova(glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #yes
Anova(glmmTMB(ave_fert_proport ~ p_h_control + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ incubation_time + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ log(sperm_egg_ratio) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_females + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_males + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ taxonomic_group + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no

# Echino model, all pH data
model.echinoderm <- glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude,  weights = 1/(w+1)^2)
Anova(model.echinoderm)
summary(model.echinoderm)

predict.echinoderm <- predict(model.echinoderm, newdata = subset(new.data, phylum=="Echinoderm"), se.fit = TRUE, type="response")
predict.echinoderm.df <- predict.echinoderm %>%
  as.data.frame() %>%
  cbind(subset(new.data, phylum=="Echinoderm"))

# Echino model, pH 7.6 and greater 
model.echinoderm7.6 <- glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.6) %>% filter(phylum=="Echinoderm"), beta_family(link="logit"), na.action=na.exclude,  weights = 1/(w+1)^2)
Anova(model.echinoderm7.6)
summary(model.echinoderm7.6)

predict.echinoderm7.6 <- predict(model.echinoderm7.6, newdata = subset(new.data.7.6, phylum=="Echinoderm"), se.fit = TRUE, type="response")
predict.echinoderm.df7.6 <- predict.echinoderm7.6 %>%
  as.data.frame() %>%
  cbind(subset(new.data.7.6, phylum=="Echinoderm"))

# Inspect residuals 
aa5 <- augment(model.echinoderm, data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm"))
ggplot(aa5, aes(x=.fitted,y=.resid)) + 
    geom_point() + 
  geom_smooth()

aa5.7.6 <- augment(model.echinoderm7.6, data=drop_na(data.fert, w) %>% filter(phylum=="Echinoderm") %>% filter(p_h_experimental>=7.6))
ggplot(aa5.7.6, aes(x=.fitted,y=.resid)) + 
    geom_point() + 
  geom_smooth()

(plot.echino <- ggplot() + 
  geom_jitter(data=drop_na(data.fert, w) %>% 
                filter(phylum=="Echinoderm"), aes(x=pH_delta, y=ave_fert_proport), size=1.2, width=0.03, col="#92c5de") +
  ggtitle("(d) Echinoderm") + 
  xlab("Delta pH") + ylab("Proportion fertilization success") +
  theme_minimal() + 
  coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
  theme(plot.title = element_text(hjust = 0.5, size=13, colour="gray15")) +
geom_ribbon(data = predict.echinoderm.df, 
              aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
              linetype=9, alpha=0.3, fill="#fff2ae") + 
     geom_line(data = predict.echinoderm.df, aes(x=pH_delta, y=fit), 
            col="gray30", linetype=2) + 
    theme(legend.position = "none") +
  geom_label(aes(x=-1.4, y=0.29), label=paste("Model with full pH range:\nχ2 p-value =",
                       round(Anova(model.echinoderm)[,"Pr(>Chisq)"], digits =6), sep=" "),
             colour="gray15", size=5, alpha=0.3, fill="#fff2ae") +
   geom_ribbon(data = predict.echinoderm.df7.6, 
              aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
              linetype=0, alpha=0.1, fill="springgreen3") +
   geom_line(data = predict.echinoderm.df7.6, 
                 aes(x=pH_delta, y=fit), 
                 col="gray30", linetype=1) +
   geom_label(aes(x=-1.2, y=0.8,
            label=paste("Model with pH ≥7.6:\nχ2 p-value =", round(Anova(model.echinoderm7.6)[,"Pr(>Chisq)"], digits =4), sep=" ")), 
            colour="gray15", size=5, alpha=0.1, fill="springgreen3"))


  # geom_line(data = predict.echinoderm.df, aes(x=pH_delta, y=fit), col="#92c5de") +
  # geom_ribbon(data = predict.echinoderm.df, aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), linetype=2, alpha=0.1, col="#92c5de") + 
  # annotate(geom="text", x=-1.5, y=0.83, size=3, colour="gray20", label=paste("χ2 p-value =\n", round(Anova(model.echinoderm)[,"Pr(>Chisq)"], digits = 3), sep=" "))


```

```{r}
(plot.echino <- ggplot() + 
  geom_jitter(data=drop_na(data.fert, w) %>% 
                filter(phylum=="Echinoderm"), 
              aes(x=pH_delta, y=ave_fert_proport), size=1.2, width=0.03, col="#92c5de") +
  ggtitle("(b) Echinoderm") + 
  xlab("Delta pH") + ylab("Proportion fertilization success") +
  theme_minimal() + 
  coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +
  theme(plot.title = element_text(hjust = 0.5, size=15, colour="gray15"), panel.grid.minor = element_blank()) +
geom_ribbon(data = predict.test.df.df %>% filter(phylum=="Echinoderm"), 
              aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
              linetype=9, alpha=0.3, fill="gray70") + 
     geom_line(data = predict.test.df.df %>% filter(phylum=="Echinoderm"), aes(x=pH_delta, y=fit), 
            col="gray30", linetype=1) + 
    theme(legend.position = "none") +
  geom_label(aes(x=-1.6, y=0.4), label=paste("z-score =", round(best.coef[best.coef$term=="phylumEchinoderm:pH_delta","statistic"], digits =2),
    "\np =", round(best.coef[best.coef$term=="phylumEchinoderm:pH_delta","p.value"], digits =9), sep=" "),
            colour="gray25", alpha=0.3,  fill=NA, size=4, label.size = NA))
   # geom_ribbon(data = predict.test.df.df.7.6 %>% filter(phylum=="Echinoderm"), 
   #            aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
   #            linetype=0, alpha=0.1, fill="springgreen3") +
   # geom_line(data = predict.test.df.df.7.6 %>% filter(phylum=="Echinoderm"),
   #               aes(x=pH_delta, y=fit), 
   #               col="gray30", linetype=1) +
   # geom_label(aes(x=-1.2, y=0.8,
   #          label=paste("Model with pH ≥7.6:\np-value =", round(best7.6.coef[best7.6.coef$term=="phylumEchinoderm:pH_delta","p.value"], digits =3), sep=" ")), 
   #          colour="gray15", size=5, alpha=0.1, fill="springgreen3")
  #)
```

### Mollusc  

```{r}
Anova(glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #yes (but close!)
Anova(glmmTMB(ave_fert_proport ~ p_h_control + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ incubation_time + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ log(sperm_egg_ratio) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_females + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ number_males + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
Anova(glmmTMB(ave_fert_proport ~ taxonomic_group + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no

AIC(glmmTMB(ave_fert_proport ~ log(sperm_egg_ratio)*pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(sperm_egg_ratio) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l)*pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(sperm_per_m_l) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(number_females)*pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
AIC(glmmTMB(ave_fert_proport ~ log(number_females) + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no

model.mollusc <- glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude,  weights = 1/(w+1)^2)
Anova(model.mollusc)
summary(model.mollusc) 

predict.mollusc <- predict(model.mollusc, newdata = subset(new.data, phylum=="Mollusc"), se.fit = TRUE, type="response")
predict.mollusc.df <- predict.mollusc %>%
  as.data.frame() %>%
  cbind(subset(new.data, phylum=="Mollusc"))

# Model with values 7.6 and greater 
model.mollusc7.6 <- glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.6) %>% filter(phylum=="Mollusc"), beta_family(link="logit"), na.action=na.exclude,  weights = 1/(w+1)^2)
Anova(model.mollusc7.6)
summary(model.mollusc7.6) 

predict.mollusc7.6 <- predict(model.mollusc7.6, newdata = subset(new.data.7.6, phylum=="Mollusc"), se.fit = TRUE, type="response")
predict.mollusc.df7.6 <- predict.mollusc7.6 %>%
  as.data.frame() %>%
  cbind(subset(new.data.7.6, phylum=="Mollusc"))

# Inspect residuals 
aa5 <- augment(model.mollusc, data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc"))
ggplot(aa5, aes(x=.fitted,y=.resid)) + 
    geom_point() + 
  geom_smooth()

aa5.7.6 <- augment(model.mollusc7.6, data=drop_na(data.fert, w) %>% filter(phylum=="Mollusc") %>% filter(p_h_experimental>=7.6))
ggplot(aa5.7.6, aes(x=.fitted,y=.resid)) + 
    geom_point() + 
  geom_smooth()


(plot.mollusc <- 
ggplot() + 
  geom_jitter(data=drop_na(data.fert, w) %>% 
                filter(phylum=="Mollusc"), aes(x=pH_delta, y=ave_fert_proport), size=1.2, width=0.03, col="#0571b0") +
  ggtitle("(e) Mollusc") + 
  xlab("Delta pH") + ylab("Proportion fertilization success") + #ylab(NULL) +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size=13, colour="gray15")) +
  coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +

  geom_ribbon(data = predict.mollusc.df, 
              aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
              linetype=9, alpha=0.3, fill="#fff2ae") + 
     geom_line(data = predict.mollusc.df, aes(x=pH_delta, y=fit), 
            col="gray30", linetype=2) + 
    theme(legend.position = "none") +
  geom_label(aes(x=-1.3, y=0.4), label=paste("Model with full pH range:\nχ2 p-value =",
                       round(Anova(model.mollusc)[,"Pr(>Chisq)"], digits =4), sep=" "),
             colour="gray15", size=5, alpha=0.3, fill="#fff2ae") +
   geom_ribbon(data = predict.mollusc.df7.6, 
              aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
              linetype=0, alpha=0.1, fill="springgreen3") +
   geom_line(data = predict.mollusc.df7.6, 
                 aes(x=pH_delta, y=fit), 
                 col="gray30", linetype=1) +
   geom_label(aes(x=-1.1, y=0.9,
            label=paste("Model with pH ≥7.6:\nχ2 p-value =", round(Anova(model.mollusc7.6)[,"Pr(>Chisq)"], digits =2), sep=" ")), 
            colour="gray15", alpha=0.1, fill="springgreen3", size=5))

```

```{r}
(plot.mollusc <- 
ggplot() + 
  geom_jitter(data=drop_na(data.fert, w) %>% 
                filter(phylum=="Mollusc"), aes(x=pH_delta, y=ave_fert_proport), size=1.2, width=0.03, col="#0571b0") +
  ggtitle("(c) Mollusc") + 
  xlab("Delta pH") + ylab("Proportion fertilization success") + #ylab(NULL) +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size=15, colour="gray15"), panel.grid.minor = element_blank()) +
  coord_cartesian(ylim = c(0, 1), xlim =c(-2,0)) +

  geom_ribbon(data = predict.test.df.df %>% filter(phylum=="Mollusc"), 
              aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
              linetype=9, alpha=0.3, fill="gray70") + 
     geom_line(data = predict.test.df.df %>% filter(phylum=="Mollusc"), aes(x=pH_delta, y=fit), 
            col="gray30", linetype=1) + 
    theme(legend.position = "none") +
  geom_label(aes(x=-1.3, y=0.4), label=paste("z-score =", round(best.coef[best.coef$term=="phylumMollusc:pH_delta","statistic"], digits =2),
    "\np =", round(best.coef[best.coef$term=="phylumMollusc:pH_delta","p.value"], digits =2),sep=" "),
            colour="gray25", alpha=0.3,  fill=NA, size=4, label.size = NA))
# geom_ribbon(data = predict.test.df.df.7.6 %>% filter(phylum=="Mollusc"), 
   #            aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), 
   #            linetype=0, alpha=0.1, fill="springgreen3") +
   # geom_line(data = predict.test.df.df.7.6 %>% filter(phylum=="Mollusc"), 
   #               aes(x=pH_delta, y=fit), 
   #               col="gray30", linetype=1) +
   # geom_label(aes(x=-1.1, y=0.9,
   #          label=paste("Model with pH ≥7.6:\np-value =", round(best7.6.coef[best7.6.coef$term=="phylumMollusc:pH_delta","p.value"], digits =2), sep=" ")), 
   #          colour="gray15", alpha=0.1, fill="springgreen3", size=5)
  #)
```


```{r}
#gg.both + ylab(NULL) + xlab(NULL)+ guides(colour = guide_legend(override.aes = list(size=6))), 
(all.plots <- ggarrange(
                      plot.cnidarian + ylab(NULL) + xlab(NULL),
                       plot.echino + ylab(NULL) + xlab(NULL), 
                       plot.mollusc + ylab(NULL) + xlab(NULL),  
                       ncol=2, nrow=2,
                       common.legend = TRUE, legend="top"))
#all.plots <- ggarrange(plot.cnidarian + ylab(NULL),  plot.echino + ylab(NULL), plot.mollusc + rremove("y.text"), ncol=1, nrow=3)
tiff(file = "fertilization-all-figures-20210308.tiff", width=3000, height=2000, res=250)
annotate_figure(all.plots, left = text_grob("Proportion Fertilization Success", color = "gray15", rot = 90))
dev.off()

png(file = "fertilization-all-figures-20210308.png", width=3000, height=2000, res=2500)
annotate_figure(all.plots, left = text_grob("Proportion Fertilization Success", color = "gray15", rot = 90))
dev.off()

jpeg(file = "fertilization-all-figures-20210308.jpeg", width=4000, height=3000, res=400)
annotate_figure(all.plots, left = text_grob("Proportion Fertilization Success", color = "gray15", rot = 90))
dev.off()

pdf(file = "fertilization-all-figures-20210308.pdf", width=12, height=8)
annotate_figure(all.plots, left = text_grob("Proportion Fertilization Success", color = "gray15", rot = 90))
dev.off()

#add the following to remove x and y axis labels: ` + rremove("x.text") + rremove("y.text")`
# add the following to add plot labels: `, labels=c("A", "B", "C", "D")`
```


### Crustacean  (BONEYARD, not using for now)

```{r}
# Anova(glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.0) %>% filter(phylum=="Crustacean"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
# Anova(glmmTMB(ave_fert_proport ~ p_h_control + (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.0) %>% filter(phylum=="Crustacean"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
# Anova(glmmTMB(ave_fert_proport ~ incubation_time + (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.0) %>% filter(phylum=="Crustacean"), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no
# 
# model.crustacean <- glmmTMB(ave_fert_proport ~ pH_delta + (1|study), data=subset(drop_na(data.fert, w), p_h_experimental>=7.0) %>% filter(phylum=="Crustacean"), beta_family(link="logit"), na.action=na.exclude,  weights = 1/(w+1)^2)
# Anova(model.crustacean)
# summary(model.crustacean) 
# 
# predict.crustacean <- predict(model.crustacean, newdata = subset(new.data, phylum=="Crustacean"), se.fit = TRUE, type="response")
# predict.crustacean.df <- predict.crustacean %>%
#   as.data.frame() %>%
#   cbind(subset(new.data, phylum=="Crustacean"))
# 
# plot.crustacean <- ggplot() + 
#   geom_jitter(data=subset(drop_na(data.fert, w), p_h_experimental>=7.0) %>% 
#                 filter(phylum=="Crustacean"), aes(x=pH_delta, y=ave_fert_proport), size=1.2, width=0.03, col="#f4a582") +
#   ggtitle("C. Crustacean") + 
#   xlab(NULL) + ylab(NULL) +
#   theme_minimal() + 
#   theme(plot.title = element_text(hjust = 0.5, size=13, colour="gray30")) +
#   coord_cartesian(ylim = c(0, 1), xlim =c(6,8.5)) +
#   geom_line(data = predict.crustacean.df, aes(x=pH_delta, y=fit), col="#f4a582") +
#   geom_ribbon(data = predict.crustacean.df, aes(x=pH_delta, ymin=fit-se.fit, ymax=fit+se.fit), linetype=2, alpha=0.1, col="#f4a582")  + 
#   annotate(geom="text", x=6.5, y=0.85, size=3.5, colour="gray20", label=paste("χ2 p-value =\n", round(Anova(model.crustacean)[,"Pr(>Chisq)"], digits = 3), sep=" "))
# print(plot.crustacean)
```

## Additional analysis steps, for posterity: inspect candidate covariates - are these important experimental design factors?  

### convert candidate covariates to numeric 

```{r}
data.fert <- data.fert %>%
  mutate_at(vars(number_trials_p_h, incubation_time, sperm_per_m_l, sperm_egg_ratio, number_females, number_males), as.numeric) 
```

### Test Control pH

```{r}
car::Anova(covariates1 <- glmmTMB(ave_fert_proport ~ p_h_control*pH_delta, data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no interaction 
ggplotly(
  ggplot(data.fert, aes(x=p_h_control, y=ave_fert_proport)) + 
    geom_jitter(aes(color = pH_delta, label=common_name), size=2.2, pch=19) + ggtitle("% Fertilization ~ Control pH\nsign. interaction") + 
    scale_color_gradientn(colours = rainbow(5))) 
#    scale_color_gradient(low = "red", high = "blue"))
```

### Test Insemination time 

```{r}
car::Anova(covariates2 <- glmmTMB(ave_fert_proport ~  incubation_time*pH_delta, data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #no interaction  
ggplotly(
  ggplot(data.fert, aes(x=incubation_time, y=ave_fert_proport)) + 
    geom_point(aes(color = pH_delta, label=common_name), size=2.2, pch=19) + ggtitle("% Fertilization ~ Insemination Time\nsign. interaction_") + 
    scale_color_gradientn(colours = rainbow(5))) 
#    scale_color_gradient(low = "red", high = "blue"))
```

### Test sperm concentration 

```{r}
car::Anova(covariates3 <- glmmTMB(ave_fert_proport ~ log(sperm_per_m_l)*pH_delta, data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #not sign 
ggplotly(ggplot(data.fert, aes(x=log(sperm_per_m_l), y=ave_fert_proport)) + 
           geom_point(aes(color = pH_delta, label=common_name), size=2.2, pch=19) + 
           ggtitle("% Fertilization ~ Sperm Concentration\nnot sign.") + 
          scale_color_gradientn(colours = rainbow(5))) 
#           scale_color_gradient(low = "red", high = "blue"))
```

### Test sperm:egg ratio 

```{r}
car::Anova(covariates4 <- glmmTMB(ave_fert_proport ~ log(sperm_egg_ratio)*pH_delta, data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #not sign 
ggplotly(ggplot(data.fert, aes(x=log(sperm_egg_ratio), y=ave_fert_proport)) + 
           geom_point(aes(color = pH_delta, label=common_name), size=2.2, pch=19) + 
           ggtitle("% Fertilization ~ Sperm:Egg Ratio\nnot sign.") + 
    scale_color_gradientn(colours = rainbow(5))) 
#           scale_color_gradient(low = "red", high = "blue"))
```

### Test no. females used for experimental eggs 

```{r}
car::Anova(covariates5 <- glmmTMB(ave_fert_proport ~  number_females*pH_delta, data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #not sign.
ggplotly(ggplot(data.fert, aes(x=number_females, y=ave_fert_proport)) + 
           geom_point(aes(color = pH_delta, label=common_name), size=2.2, pch=19) + 
           ggtitle("% Fertilization ~ No. Females\nno interaction") + 
    scale_color_gradientn(colours = rainbow(5))) 
#           scale_color_gradient(low = "red", high = "blue"))
```

### Test no. males used for experimental eggs 

```{r}
car::Anova(covariates6 <- glmmTMB(ave_fert_proport ~  number_males*pH_delta, data=drop_na(data.fert, w), beta_family(link="logit"), na.action=na.exclude, weights = 1/(w+1)^2)) #not sign. 
ggplotly(ggplot(data.fert, aes(x=number_males, y=ave_fert_proport)) + 
           geom_point(aes(color = pH_delta, label=common_name), size=2.2, pch=19) + 
           ggtitle("% Fertilization ~ No. Males\nsign. interaction") + 
     scale_color_gradientn(colours = rainbow(5))) 
#          scale_color_gradient(low = "red", high = "blue"))
```

